Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-08-16 ehp_revision/response_to_reviewers.Rmd

**Response:**

\begin{shaded}
\textbf{Reviewer 1 (R1) Comment 1:}
I very much appreciate the rationale for authors' decision to focus at the
county level, especially given the available health-related data. But, since
tropical cyclones don't necessarily have consistent impacts across an entire
county, I think the limitations of this decision are worthy of further
discussion in the discussion section.
\end{shaded}

**Response:**

This is an excellent point. We have added text in the Limitations section of the
Discussion on the potential limitations of using aggregated, county-level
exposure data in a research study:

> **Text added to Discussion (added text in bold):** "Second, these data are
aggregated to the county level. **This spatial scale allows for easy integration
with health outcome data aggregated at the county level. Such aggregated or
ecological data is often used for disaster epidemiology, as aggregated data may
be easier to access than individual-level data, especially at a scale that
covers many locations and a long time period and so allows higher statistical
power and a broader range of exposure levels within the study
[@wakefield2008overcoming].**

@@

> "**Aggregated data can be used to infer contextual level associations---for
example, the association between county-level exposure to a storm hazard and
county-wide rates of a health outcome. However, ecological data is also
sometimes used to infer individual-level associations (e.g., the association
between personal exposure to a storm hazard and personal risk of  experiencing
the health outcome). Individual-level inference from ecological/aggregated data
is susceptible to ecological bias [@greenland1994invited; @portnov2007ecological;
@idrovo2011three]. Researchers who use the data provided here for ecological
studies---with the aim of making individual-level inferences---should be aware
of this potential and could explore approaches for minimizing risk of ecological
bias (e.g., @wakefield2008overcoming).**"

\begin{shaded}
\textbf{R1 Comment 2:}
Are there opportunities to expand this approach internationally? Some decisions
(e.g., county-level) data may restrict cross-country comparisons. Can the
authors discuss this? 
\end{shaded}

**Response:**

While there would be some limitations in comparisons based on differences in the
scale of county-equivalents, many countries affected by tropical cyclones do
have geopolitical areas that are fairly comparable to US counties, like
municipalities in Mexico, districts in India. There would be a few challenges,
however, in developing the exposure dataset for the hazards that we cover in the
US in the data presented in this paper. We have added text to the paper's
Discussion on opportunities and barriers to expanding this approach
internationally:

> Text added to the Discussion (added text in bold): 
"**This dataset is limited to the contiguous US. Some exposure estimates would
be fairly straightforward to extend internationally. The precipitation data is
extracted and aggregated to the county level from a re-analysis data product.
While the re-analysis product used here (NLDAS-2) only covers the contiguous US,
other similar re-analysis products, as well as other types of precipitation
datasets, have global coverage [@sun2018review]. The wind data are generated
based on a model that is currently US-focused [@stormwindmodel], but could be
extended to other areas, although this would require adding new land/sea masks
within the associated software, as well as accounting for differences across
storm basins in wind averaging periods [@harper2010guidelines] and in the
direction of cyclonic winds in the Northern versus Southern Hemisphere. Further,
since the core of the wind model was developed based on data from Atlantic-basin
storms [@willoughby2006parametric], an extension to other areas should include
separate validation and calibration to ensure it performs appropriately in those
settings. Other wind field modeling software is also available that already
provides a global coverage, like Geoscience Australia's Tropical Cyclone Risk
Model (http://geoscienceaustralia.github.io/tcrm/). For tornado and flood
events, the data described in this paper drew on a US-focused storm events
database, and so international extension of data on these hazards would require
access to similar databases covering other countries. Finally, the relevant
geopolitical boundaries to use for aggregation would vary by country (e.g.,
municipalities in Mexico, districts in India).**"

### 2020-08-16 ehp_revision/writing/ehp_discussion.tex
Work on cleaning up a response

>>>>

\textbf{This dataset is limited to the contiguous US. The precipitation data is
extracted and aggregated to the county level from a re-analysis data product.
While the re-analysis product used here (NLDAS-2) only covers the contiguous
US, other similar re-analysis products, as well as other types of precipitation
datasets, have global coverage \parencite{sun2018review}. The wind data are
generated based on a model that is currently US-focused
\parencite{stormwindmodel}, but could be extended to other areas, although this
would require adding new land/sea masks within the associated software, as well
as accounting for differences across storm basins in wind averaging periods
\parencite{harper2010guidelines} and in the direction of cyclonic winds in the
Northern versus Southern Hemisphere. Further, since the core of the wind model
was developed based on data from Atlantic-basin storms
\parencite{willoughby2006parametric}, an extension to other areas should
include separate validation and calibration to ensure it performs appropriately
in those settings. Other wind field modeling software is also available that
already provides a global coverage, like Geoscience Australia's Tropical
Cyclone Risk Model (http://geoscienceaustralia.github.io/tcrm/). For tornado
and flood events, the data described in this paper drew on a US-focused storm
events database, and so international extension of data on these hazards would
require access to similar databases covering other countries. Finally, the
relevant geopolitical boundaries to use for aggregation would vary by country
(e.g., municipalities in Mexico, districts in India).}
